---
title: "Citations of women artists in an Art History book"
format: html
---

```{r load packages and data}
#| echo: false
#| eval: false
library(tidyverse)
raw_data_artists <- read_csv("data-raw/artists.csv")
```

## Introduction

The books History of Art and Art Through the Ages are two of the most widely used art history textbooks in the United States. They are used in college courses and are considered to be authoritative sources on the history of art. However, the citation of women artists is still very low in these books.

## Artistic representation by ethnicity

When exploring artists' ethnicity, we found that the majority of artists cited in the books are white. This is not surprising, as the art world has historically been dominated by white artists. However, it is important to note that there are many talented artists of color who are not being represented in these books.

Here's a data visualization:

```{r}
#| echo: false
female_artists_ethnicity <- 
  raw_data_artists |> 
  filter(artist_gender == "Female") |>
  group_by(artist_ethnicity, year) |>
  summarise(n = n()) 

# Plot the distribution of ethnicities

ggplot(female_artists_ethnicity,        # Data
       aes(x = as.factor(year),         # X-axis
           y = n,                       # Y-axis
           group = artist_ethnicity,    # Grouping
           color = artist_ethnicity)) + # Color
  geom_line() +                         # Make it a line plot
  theme_minimal() +                     # Theme
  labs(title = "Distribution of ethnicities of female artists cited on the book 'Art Through the Ages' throughout the years",            # Title
       y = NULL,                        # Y-axis label
       x = NULL,                        # X-axis label
       color = "Artists' ethnicity")    # Legend title
```

The `echo: false` option disables the printing of code (only output is displayed).
